Designing and Developing a Personalised Recommender System

### 2021-02-12 paper/paper.tex
spelling corrections to paper

\subsection{Data description}
The data for my recommender system was generated from the Yelp Open Dataset \cite{YelpDataset}. 
This is a subset of all the businesses, reviews, and user data on Yelp, formatted as JSON files. 
The dataset includes approximately 8,000,000 reviews of 200,000 businesses by 2,000,000 users, as well as 
additional Covid-19 related features of each business such as whether they now offer takeout or delivery. 
There are 3 sections of the dataset, with 5 JSON files in the main dataset, 1 in the photos section, and 
1 in the covid section. 
The $business.json$ file contains business data including location data, attributes, and cuisine. 
$review.json$ contains full review text data including the $user\_id$ that wrote the review and the $business\_id$ 
that the review is written for. 
The file $user.json$ holds every user's first name along with other data adn metadata which I don't use \cite{YelpDataset}. 
The data files $checkin.json$ and $tip.json$ are not used in my system. 
The dataset also includes approximately 200,000 photos but these are not relevant to my application, since 
the interface is command line only, so they were discarded. 
The covid related data from $covid\_features.json$ contains additional information about each business with regards to 
the measures they have taken due to the pandemic, such as offering delivery or takeout options or a 
special message for customers. 
Every business in the dataset is in 1 of 10 metropolitan areas in the USA and Canada 
(Montreal, Calgary, Toronto, Pittsburgh, Charlotte, Urbana-Champaign, Phoenix, Las Vegas, Madison, and Cleveland) \cite{YelpDataset}.

@@

\subsection{Hybrid scheme}
The two personalised recommender systems I implement are knowledge-based and collaborative-filtering, and 
the hybrid scheme is cascade. 
A cascade hybrid scheme works particularly well in my domain of restaurants with an emphasis on providing accurate 
predictions of restaurants which a user may like in a city they have never been to before, based on the restaurants 
they like in their home-city. 
This is because the knowledge-based system can filter the restaurants by location and by the type of food they serve, 
while the collaborative-filtering system is able to find restaurants which are similar to the ones the user has 
previously rated highly. 
So when these two systems are combined in a cascade style with the knowledge-based system as the primary recommender 
and the collaborative-filtering system as the secondary the hybrid system can find hidden similarities between 
restaurants in different cities very accurately. 
This method of hybrid recommender system (HRS) has been implemented as a restaurant recommender in the Entree 
system, giving very accurate results \cite{burke1999integrating,burke2000knowledge,burke2002hybrid,burke2007hybrid}.

\subsection{Recommendation techniques/algorithms}
The first prediction method used in this hybrid system is a knowledge-based (KB) approach, which relies on knowledge 
about each of the restaurants based on its location and the type of food that it serves. 
This approach completely eliminates the cold-start problem, a new user will still receive relevant recommendations 
for the city they are in and the type of food they in the mood for when using a KB system. 
The second prediction method is a collaborative-filtering (CF) approach, specifically Single Value Decomposition (SVD) 
matrix factorisation. 
This approach was chosen because it scales well with large datasets, which is important since my dataset has 
~120,000 entries. 
The CF technique here also introduces an element of variability in the recommendations, such that the user 
may not receive the same ordering of suggestions when they run the system multiple times with the same 
KB specifications, helping the user to try new things. 
This system allows the user to make ratings through the user interface, providing the ability to experiment with 
the system in terms of how new ratings affect the current user's recommendations as well as those of other similar users.

@@

Coverage of the system is calculated by:
\begin{equation}
    Prediction\ coverage = \frac{|I_p|}{|I|}
\end{equation} 
where $I_p$ is the set of restaurants which can be recommended and $I$ is the set of all restaurants. 
In my system the coverage is ~0.32 ($\frac{20,565}{63,944}$), this is the most appropriate metric since 
the data for previously views items does not exist, ruling out novelty and diversity metrics.

@@

\subsection{Input interface}
The system has a command line based interface, so all user input of the input is given via the command line. 
The system recognises the active user by their unique user ID, some example IDs are provided in the 'README.txt' 
file for testing and demonstration purposes. 
Only explicit user data is gathered in order to make the system more explainable and transparent, 
and users are made aware of which data is collected, how it is collected, and for which purposes. 
This data includes the user's nearest city (of the 10 available) and the type of food that 
they are in the mood for. 
The user is able to change these choices from the main menu, as well as switch to a different user 
for testing purposes. 
When the user is presented with a list of recommendations, they can then choose one that they want 
to see more information about and from here they can leave a rating, return to the list, or return to 
the main menu. 
User profiles can be updated by giving a rating of a restaurant through the system. 
Any rating given will affect future recommendations given by the system to that user 
and to other similar users.

@@

\subsection{Comparison against hybrid recommenders in related studies}
The Entree restaurant recommender system is an example of a cascade style hybrid recommender system which 
uses both knowledge-based and collaborative-filtering methods to help users find a restaurant they might like in 
a city they've never been to before \cite{burke1999integrating,burke2000knowledge,burke2002hybrid,burke2007hybrid}. 
This is very similar to the way my system works, with the biggest difference being the vastly greater amount of 
knowledge engineering that has gone into Entree. 
This additional knowledge is used in Entree, and other FindMe style systems, to give more accurate similarity assessments 
of restaurants by considering factors such as price and quality of experience as well as location and cuisine, 
and by arranging these factors hierarchically. 
For example, Entree arranges these as: cuisine, price, quality of experience, others, but other systems allow the 
user to specify this order themselves. 
This is part of the reason why Entree would outperform this system.

>>>>

\subsection{Data description}
The data for my recommender system was generated from the Yelp Open Dataset \cite{YelpDataset}. 
This is a subset of all the businesses, reviews, and user data on Yelp, formatted as JSON files. 
The dataset includes approximately 8,000,000 reviews of 200,000 businesses by 2,000,000 users, as well as 
additional Covid-19 related features of each business such as whether they now offer takeout or delivery. 
There are 3 sections of the dataset, with 5 JSON files in the main dataset, 1 in the photos section, and 
1 in the covid section. 
The $business.json$ file contains business data including location data, attributes, and cuisine. 
$review.json$ contains full review text data including the $user\_id$ that wrote the review and the $business\_id$ 
that the review is written for. 
The file $user.json$ holds every user's first name along with other data and metadata which I don't use \cite{YelpDataset}. 
The data files $checkin.json$ and $tip.json$ are not used in my system. 
The dataset also includes approximately 200,000 photos but these are not relevant to my application, since 
the interface is command line only, so they were discarded. 
The covid related data from $covid\_features.json$ contains additional information about each business with regards to 
the measures they have taken due to the pandemic, such as offering delivery or takeout options or a 
special message for customers. 
Every business in the dataset is in 1 of 10 metropolitan areas in the USA and Canada 
(Montreal, Calgary, Toronto, Pittsburgh, Charlotte, Urbana-Champaign, Phoenix, Las Vegas, Madison, and Cleveland) \cite{YelpDataset}.

@@

\subsection{Hybrid scheme}
The two personalised recommender systems I implement are knowledge-based and collaborative-filtering, and 
the hybrid scheme is cascade. 
A cascade hybrid scheme works particularly well in my domain of restaurants with an emphasis on providing accurate 
predictions of restaurants which a user may like in a city they have never been to before, based on the restaurants 
they like in their home-city. 
This is because the knowledge-based system can filter the restaurants by location and by the type of food they serve, 
while the collaborative-filtering system is able to find restaurants which are similar to the ones the user has 
previously rated highly. 
So when these two systems are combined in a cascade style with the knowledge-based system as the primary recommender 
and the collaborative-filtering system as the secondary the hybrid system can find hidden similarities between 
restaurants in different cities accurately. 
This method of hybrid recommender system (HRS) has been implemented as a restaurant recommender in the Entree 
system, giving very accurate results \cite{burke1999integrating,burke2000knowledge,burke2002hybrid,burke2007hybrid}.

\subsection{Recommendation techniques/algorithms}
The first prediction method used in this hybrid system is a knowledge-based (KB) approach, which relies on knowledge 
about each of the restaurants based on its location and the type of food that it serves. 
This approach completely eliminates the cold-start problem, a new user will still receive relevant recommendations 
for the city they are in and the type of food they in the mood for when using a KB system. 
The second prediction method is a collaborative-filtering (CF) approach, specifically Single Value Decomposition (SVD) 
matrix factorisation. 
This approach was chosen because it scales well with large datasets, which is important since my dataset has 
roughly 120,000 entries. 
The CF technique here also introduces an element of variability in the recommendations, such that the user 
may not receive the same ordering of suggestions when they run the system multiple times with the same 
KB specifications, helping the user to try new things. 
This system allows the user to make ratings through the user interface, providing the ability to experiment with 
the system in terms of how new ratings affect the current user's recommendations as well as those of other similar users.

@@

Coverage of the system is calculated by:
\begin{equation}
    Prediction\ coverage = \frac{|I_p|}{|I|}
\end{equation} 
where $I_p$ is the set of restaurants which can be recommended and $I$ is the set of all restaurants. 
In my system the coverage is ~0.32 ($\frac{20,565}{63,944}$), this is the most appropriate metric since 
the data for previously viewed items does not exist, ruling out novelty and diversity metrics.

@@

\subsection{Input interface}
The system has a command line based interface, so all user input is given via the command line. 
The system recognises the active user by their unique user ID. 
Some example IDs are provided in the 'README.txt' file for testing and demonstration purposes. 
Only explicit user data is gathered in order to make the system more explainable and transparent, 
and users are made aware of which data is collected, how it is collected, and for which purposes. 
This data includes the user's nearest city (of the 10 available) and the type of food that 
they are in the mood for. 
The user is able to change these choices from the main menu, as well as switch to a different user 
for testing purposes. 
When the user is presented with a list of recommendations, they can then choose one that they want 
to see more information about and from here they can leave a rating, return to the list, or return to 
the main menu. 
User profiles can be updated by giving a rating of a restaurant through the system. 
Any rating given will affect future recommendations given by the system to that user 
and to other similar users.

@@

\subsection{Comparison against hybrid recommenders in related studies}
The Entree restaurant recommender system is an example of a cascade style hybrid recommender system which 
uses both knowledge-based and collaborative-filtering methods to help users find a restaurant they might like in 
a city they've never been to before \cite{burke1999integrating,burke2000knowledge,burke2002hybrid,burke2007hybrid}. 
This is very similar to the way my system works, with the biggest difference being the vastly greater amount of 
knowledge engineering that has gone into Entree. 
This additional knowledge is used in Entree, and other FindMe style systems, to give more accurate similarity assessments 
of restaurants by considering factors such as price and quality of experience as well as location and cuisine, 
and by arranging these factors hierarchically. 
For example, Entree arranges these as: cuisine, price, and quality of experience, in descending order of importance 
and other systems allow the user to specify this order themselves. 
This is part of the reason why Entree would outperform this system.
